Review of Assigned Readings

### 2017-12-26 documentation/documentation.tex
added documentation/documentation.tex

\documentclass[a4paper,american,12pt]{article}
\usepackage{graphicx}
\graphicspath{ {images/} }

%% Language and font encodings
\usepackage[utf8]{inputenc}

@@

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[noconfigs,british]{babel}

@@

    \begin{document}
    \begin{titlepage}
        \centering
        {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
        \vspace{2cm}
        {\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
		\vspace{1.5cm}        
        {\large\today\par}
        \vspace{1.5cm}
        {\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
        \vspace{1.5cm}
        {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}

        \begin{spacing}{1.5}
        \vspace{1cm}
        {Fall Term 2017 \par}
        \vspace{1cm}
        Supervisor\\
        {Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par} 
        \end{spacing}
    \end{titlepage}

    \begin{abstract}
    \pagenumbering{Roman}
    \begin{spacing}{1.5}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\graphicspath{ {images/} }

%% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

@@

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{setspace}

@@

    \begin{document}
    \begin{titlepage}
        \centering
        {\scshape\LARGE University of St.Gallen \par}
        \vspace{1cm}
        {\scshape\Large Software Engineering for Economists \par}
        \vspace{1.3cm}
        {\huge\bfseries Name of Project  \par}
        {\Large\itshape Documentation\par}
        \vspace{3cm}
        {\Large\itshape Joël Sonderegger\par}
        \begin{spacing}{1.2}
        joel.sonderegger{@}student.unisg.ch\linebreak
        11-495-488\linebreak

        \vspace{1cm}
        Fall Term 2017
        \vfill
        Supervisor
        \linebreak
        Prof. Dr. Philipp \textsc{Zahn}
        \linebreak
        Department of Economics
        \end{spacing}

        \vfill

    % Bottom of the page
     {\large \today\par}

    \end{titlepage}
    \begin{abstract}
    \pagenumbering{Roman}
    \begin{spacing}{1.5}
